Blue Hunters: Bluetooth RSSI Locator Robots

### 2018-02-01 article/article.tex
start bib

\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex

@@

\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}

@@

The PIC commmunicates with the IMU via I2C. The IMU includes a breakout
board for the QFN MPU-9250 module, which itself includes 2 dies. One
contains the 3-axis gyroscope and 3-axis accelerometer, which were not
used in this project, and the other die is the AK8963 3-axis
magnetometer (compass).

@@

\begin{itemize}
\tightlist
\item
  \href{https://www.invensense.com/wp-content/uploads/2015/02/PS-MPU-9250A-01-v1.1.pdf}{MPU-9250}
  and
  \href{https://cdn.sparkfun.com/assets/learn_tutorials/5/5/0/MPU-9250-Register-Map.pdf}{its
  register map}.
\item
  \href{https://www.akm.com/akm/en/file/datasheet/AK8963C.pdf}{3-axis
  Electronic Compass on IMU}.
\item
  \href{http://www.jnhuamao.cn/bluetooth40_en.zip}{HM-10 (Bluetooth
  breakout module \& firmware)}. The ZIP contains the original data
  sheet, as well as other documentation.
  \href{http://fab.cba.mit.edu/classes/863.15/doc/tutorials/programming/bluetooth/bluetooth40_en.pdf}{MIT
  has a PDF} available, which may me out of date, but is easier to get
  to.
\item
  \href{http://ww1.microchip.com/downloads/en/DeviceDoc/60001168J.pdf}{PIC32MX250}.
\end{itemize}

@@

>>>>

@@

@@

The PIC commmunicates with the IMU via I2C. The IMU includes a breakout
board for the QFN MPU-9250 \cite{mpu9250datasheet} \cite{mpu9250regmap} module, which itself includes 2 dies. One
contains the 3-axis gyroscope and 3-axis accelerometer, which were not
used in this project, and the other die is the AK8963 3-axis
magnetometer (compass).

@@

\begin{itemize}
\tightlist
\item
  \href{https://www.akm.com/akm/en/file/datasheet/AK8963C.pdf}{3-axis
  Electronic Compass on IMU}.
\item
  \href{http://www.jnhuamao.cn/bluetooth40_en.zip}{HM-10 (Bluetooth
  breakout module \& firmware)}. The ZIP contains the original data
  sheet, as well as other documentation.
  \href{http://fab.cba.mit.edu/classes/863.15/doc/tutorials/programming/bluetooth/bluetooth40_en.pdf}{MIT
  has a PDF} available, which may me out of date, but is easier to get
  to.
\item
  \href{http://ww1.microchip.com/downloads/en/DeviceDoc/60001168J.pdf}{PIC32MX250}.
\end{itemize}

@@

\bibliography{references}{}
\bibliographystyle{ieeetr}
